---
title: "R Notebook"
output: html_notebook
---
Loading data. 

```{r}
df <- read.csv("/home/laidhimonthegreen/Документы/Учёба/social networks/Final_SN_Project/drama_dataset.csv", sep=",")
```

```{r}
library(ggplot2)
library(dplyr)
df %>% group_by(gender) %>%
  summarise(count=n())
```
232 male, 102 female. Unbalanced corpus.
```{r}
df %>% group_by(importance) %>%
  summarise(count=n())
```
123 Lead, 135 Secondary, 75 Episode, 4 - Group of People (Народ, Хор etc.)
```{r}
df %>% group_by(gender) %>%
  summarise(degree=signif(mean(degree_cent), digits=3),
  betw=signif(mean(between_cent), digits=2),
  PR=signif(mean(pagerank), digits=2),
  word_amount=signif(mean(relative_words), digits=2))
```
It can be seen that there is almost no difference between male and female characters. Group characters show significantly less amount of words, but this category is not that representative.
```{r}
df %>% group_by(importance) %>%
    summarise(degree=signif(mean(degree_cent), digits=3),
    betw=signif(mean(between_cent), digits=2),
    PR=signif(mean(pagerank), digits=2),
    word_amount=signif(mean(relative_words), digits=2))
```
Looks valid. Let us look at boxplots.
```{r}
boxplot(df$degree_cent ~ df$importance,
main="Degree centrality", xlab="Character Importance")
```
```{r}
boxplot(df$between_cent ~ df$importance,
main="Betweenness centrality", xlab="Character Importance")
```
```{r}
boxplot(df$pagerank ~ df$importance,
main="Pagerank", xlab="Character Importance")
```
```{r}
boxplot(df$relative_words ~ df$importance,
main="Word amount", xlab="Character Importance")
```
It seems that all four variables can be used to determine the importance of the character. 
